Figures

### 2019-11-11 manuscript/figures.Rmd
warnings and messages now not included. Sorted library loading errors
figures included within manuscript

---
title: Figures
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE)
```

```{r library_load,cache=FALSE}
source('../code/library_load.R')
```

```{r prep}
source('../code/data_prep.R')
```

@@

```{r descriptor_contributions, fig.height = 5,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures. a) Phenotypic decline index (PDI). b) Decline acuteness index (DAI)'}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots()
```

>>>>

@@

```{r descriptor_contributions, fig.height = 5,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures. a) Phenotypic decline index (PDI). b) Decline acuteness index (DAI)'}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  patchwork::wrap_plots()
```
